\documentclass[letterpaper,12pt]{article}
\usepackage{tabularx} % extra features for tabular environment
\usepackage{amsmath}  % improve math presentation
\usepackage{graphicx} % takes care of graphic including machinery
\usepackage[margin=1in,letterpaper]{geometry} % decreases margins
\usepackage{cite} % takes care of citations
\usepackage{longtable}
\usepackage{booktabs}
\usepackage[final]{hyperref} % adds hyper links inside the generated pdf file
\hypersetup{
	colorlinks=true,       % false: boxed links; true: colored links
	linkcolor=blue,        % color of internal links
	citecolor=blue,        % color of links to bibliography
	filecolor=magenta,     % color of file links
	urlcolor=blue         
}
\usepackage{blindtext}
%++++++++++++++++++++++++++++++++++++++++


\begin{document}

\title{Predict Active Regulatory Regions Using Deep Learning Models in HEK293 cell line}
\author{Michele Antonazzi}
\date{\today}
\maketitle

\begin{abstract}
In this work, we studied the prediction of active and inactive regulatory regions (promoters and enhancers) in the HEK293 cell line. 
The aim is to prove the effectiveness of deep learning models using both epigenomic and sequence data. In particular, the deep models tested are feed-forward neural network (FFNN) and convolutional neural networks (CNN), which are used on the epigenomic and sequence data respectively.
\end{abstract}

\input{introduction.tex}
\newpage

\input{models.tex}

\newpage

\input{experimental_setup.tex}

\input{experimental_results.tex}
\newpage
\begin{thebibliography}{99}

\bibitem{}
Yifeng Li, Wenqiang Shi, and Wyeth W. Wasserman. \textit{"Genome-wide
prediction of cis-regulatory regions using supervised deep learning
methods"}

\bibitem{}
Xu Min, Wanwen Zeng, Shengquan Chen, Ning Chen, Ting Chen, Rui Jiang \textit{"Predicting enhancers with deep convolutional
neural networks"}

\bibitem{}
Kelley DR, Snoek J, Rinn JL. 2016. \textit{Basset: learning the
regulatory code of the accessible genome with deep convolutional neural
networks.}

\bibitem{}
 David R. Kelley, Yakir A. Reshef, Maxwell Bileschi, David
Belanger, Cory Y. McLean, and Jasper Snoek. \textit{"Sequential regulatory
activity prediction across chromosomes with convolutional neural
networks"}

\bibitem{}
Luca Cappelletti, Alessandro Petrini, Jessica Gliozzo, Elena
Casiraghi, Max Schubach, Martin Kircher, Giorgio Valentini. \textit{"Bayesian
optimization improves tissue-specific prediction of active regulatory
regions with deep neural networks"}

\end{thebibliography}


\end{document}